Notes on $\etarho$

### 2008-09-26 docs/eta_notes/paper.tex
fixed some typos, added some clarification

We carry around three different 1D radial quantities: $\etarho$ (edge-centered), $\etarhocc$ (cell-centered), and $\divetarho$ (edge-centered).  These notes discuss when each of these is used, and how they are computed, in both plane-parallel and spherical.

@@

\subsection{Spherical}
First, construct $\eta_{\rho}^{\rm cart} = [\rho'(\Ubt\cdot\eb_r)]^{n+\half}$.  Then, $\etarhocc$ is the cell-centered average of $\eta_{\rho}^{\rm cart}$,
\begin{equation}
\etarhocc = \overline{\eta_{\rho}^{\rm cart}}.
\end{equation}
On interior faces, $\etarho$ is the average of $\etarhocc$,
\begin{equation}
\eta_{\rho,r+\half} = \frac{\eta_{\rho,r}^{\rm cc} + \eta_{\rho,r+1}^{\rm cc}}{2}.
\end{equation}
At the upper and lower boundaries, we use
\begin{eqnarray}
\eta_{\rho,0} &=& 0, \\
\eta_{\rho,{\rm nr}} &=& \eta_{\rho,{\rm nr}-1}^{\rm cc}.
\end{eqnarray}
$\divetarho$ is constructed from the cell-centered average of $\rho'^{n+1}$ as
\begin{equation}
\divetarho = -\overline{\rho'^{n+1}}/\Delta t
\end{equation}

>>>>

We carry around three different 1D radial quantities: $\etarho$ (edge-centered), $\etarhocc$ (cell-centered), and $\divetarho$ (cell-centered).  These notes discuss when each of these is used, and how they are computed, in both plane-parallel and spherical.

@@

\subsection{Spherical}
First, construct $\eta_{\rho}^{\rm cart} = [\rho'(\Ubt\cdot\eb_r)]^{n+\half}$ using:
\begin{equation}
\left[\frac{\rho^n+\rho^{n+1}}{2}-\left(\frac{\rho_0^n+\rho_0^{n+1}}{2}\right)^{\rm cart}\right] \sum_d\left(\frac{\Ubt_{\ib+\half\eb_d}^{n+\half}\cdot\eb_d+\Ubt_{\ib-\half\eb_d}^{n+\half}\cdot\eb_d}{2}\right)n_d.
\end{equation}
Then, $\etarhocc$ is the cell-centered average of $\eta_{\rho}^{\rm cart}$,
\begin{equation}
\etarhocc = \overline{\eta_{\rho}^{\rm cart}}.
\end{equation}
On interior faces, $\etarho$ is the average of $\etarhocc$,
\begin{equation}
\eta_{\rho,r-\half} = \frac{\eta_{\rho,r-1}^{\rm cc} + \eta_{\rho,r}^{\rm cc}}{2}.
\end{equation}
At the upper and lower boundaries, we use
\begin{eqnarray}
\eta_{\rho,-\half} &=& 0, \\
\eta_{\rho,{\rm nr}-\half} &=& \eta_{\rho,{\rm nr}-1}^{\rm cc}.
\end{eqnarray}
$\divetarho$ is constructed from the cell-centered average of $\rho'^{n+1} = \rho^{n+1} - \rho_0^{n+1}$ as
\begin{equation}
\divetarho = -\overline{\rho'^{n+1}}/\Delta t
\end{equation}
